Considering scale in multilayer animal social networks

### 2020-06-16 paper/manuscript.Rmd
question about last sentence

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in open and forage layers, and lower strength
in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
the rate of increase after 100 m (<!--TODO: figure XX-->). 
These results suggest the optimal social scale at
which groups should be assigned is between ~20 - 100 m based on
the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
an appropriate social scale for generating social networks in caribou and
similar species.

>>>>

# Results
Individuals in multilayer networks became more connected as the spatial distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in open and forage layers, and lower strength
in forest layers (Figure \@ref(fig:socres)). Individual graph strength increased
sharply between 5 m and 100 m in all three habitat classes followed by a plateau in
the rate of increase after 100 m (<!--TODO: figure XX-->). 
These results suggest the optimal social scale at
which groups should be assigned is between ~20 - 100 m based on
the rate at which network metrics <!--QW: which metrics?--> stabilized. For ungulates, groups are often
assigned based on 50 m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier
et al. 2019), suggesting that given similar quantities of data, ~50 m is likely
an appropriate social scale for generating social networks in caribou and
similar species. <!--QW: I'm not sure about this statement. Should it be more about 
how GPS data allows (e.g. from this study and Peignier et al; Lesmerises et al.) us to confirm 
the use of 50m buffer that has long been used for studies in the field (e.g. Lingle 2003 and 
any Clutton-Brock red deer paper that uses group size data)-->
